### 2020-04-04 Thesis/intro.tex
Corrections.

Things get even more difficult when we consider nondeterministic versions of stateless languages such as PCF.  
Naively relaxing the determinism constraint on the usual definition of an innocent strategy does not give the right notion of a nondeterministic innocent strategy \cite{TsukadaSheaves}.  
There are definitions of nondeterministic innocence due to Levy \cite{levy2014morphisms}, toTsukada and Ong \cite{TsukadaSheaves}, and, via concurrent games, to Castellan, Clairambault, Hayman and Winskel \cite{NonAngelic}, that use the concept of \emph{morphisms between plays}, but these are already some distance removed conceptually from Hyland and Ong's original paper that introduced deterministic innocent strategies.
Tsukada and Ong's paper involves a complete recasting of strategies as sheaves in order to understand what happens when we try to mix nondeterminism and innocence.

@@

We can prove continuoity of composition in general for the new language, which allows us to prove computational adequacy in the usual way.
Having done this, we then use operational methods to find a way to identify terms that should be observationally equivalent in the original sense.  
This allows us to quotient out our model for the new language to get one that is computationally adequate for the ordinary nondeterministic version.

>>>>

Things get even more difficult when we consider nondeterministic versions of stateless languages such as PCF.  
Naively relaxing the determinism constraint on the usual definition of an innocent strategy does not give the right notion of a nondeterministic innocent strategy \cite{TsukadaSheaves}.  
There are definitions of nondeterministic innocence due to Levy \cite{levy2014morphisms}, to Tsukada and Ong \cite{TsukadaSheaves}, and, via concurrent games, to Castellan, Clairambault, Hayman and Winskel \cite{NonAngelic}, that use the concept of \emph{morphisms between plays}, but these are already some distance removed conceptually from Hyland and Ong's original paper that introduced deterministic innocent strategies.
Tsukada and Ong's paper involves a complete recasting of strategies as sheaves in order to understand what happens when we try to mix nondeterminism and innocence.

@@

We can prove continuity of composition in general for the new language, which allows us to prove computational adequacy in the usual way.
Having done this, we then use operational methods to find a way to identify terms that should be observationally equivalent in the original sense.  
This allows us to quotient out our model for the new language to get one that is computationally adequate for the ordinary nondeterministic version.
